Implications of afforestation policies for global markets

### 2024-02-27 paper.Rmd
Update paper.Rmd

Table 1. Forestland by region in 2023 and estimated change by 2033
	Russia	Sub-Saharan Africa Brazil Canada Rest of South America	United States Southeast Asia Oceania EU	China Central America South Asia Other Europe North Africa & the Middle East Japan East Asia Total 
Forestland in 2023	838.1	564.7	498.2	412.8	348.5	248.4	243.9	199.2	186.7	164.6	94.6	47.8	40.2	33.8	23.7	14.5	3,959.5
Forestland in 2033	828.7	525.0	479.2	407.9	325.0	249.7	221.3	196.1	175.5	164.8	91.2	42.6	36.1	30.9	26.9	14.6	3,815.3
∆ (ha)			-9.5	-39.7	-19.0	-5.0	-23.5	1.3	-22.6	-3.1	-11.1	0.1	-3.4	-5.3	-4.1	-2.9	3.2	0.1	-144.2
∆ (%)			-1.1	-7.0	-3.8	-1.2	-6.7	0.5	-9.3	-1.5	-6.0	0.1	-3.6	-11.0	-10.1	-8.5	13.7	0.7	-3.6

>>>>

Table 1. Forestland by region in 2023 and estimated change by 2033
	Russia	Sub-Saharan Africa Brazil Canada Rest of South America	United States Southeast Asia Oceania Western & Central Europe China Central America South Asia Other Europe North Africa & the Middle East Japan East Asia Total 
Forestland in 2023	838.1	564.7	498.2	412.8	348.5	248.4	243.9	199.2	186.7	164.6	94.6	47.8	40.2	33.8	23.7	14.5	3,959.5
Forestland in 2033	828.7	525.0	479.2	407.9	325.0	249.7	221.3	196.1	175.5	164.8	91.2	42.6	36.1	30.9	26.9	14.6	3,815.3
∆ (ha)			-9.5	-39.7	-19.0	-5.0	-23.5	1.3	-22.6	-3.1	-11.1	0.1	-3.4	-5.3	-4.1	-2.9	3.2	0.1	-144.2
∆ (%)			-1.1	-7.0	-3.8	-1.2	-6.7	0.5	-9.3	-1.5	-6.0	0.1	-3.6	-11.0	-10.1	-8.5	13.7	0.7	-3.6
Note: Southeast Asia includes Brunei Darussalam, Cambodia, Indonesia, Laos, Malaysia, Myanmar, Philippines, Singapore, Thailand, Timor-Leste, and Vietnam. Oceania includes Australia, Cook Islands, Fiji, French Polynesia, Kiribati, Marshall Islands, Micronesia, Nauru, New Caledonia, New Zealand, Palau, Papua New Guinea, Samoa (Western Samoa), Solomon Islands, Tonga, Tuvalu, and Vanuatu. Rest of South America includes 
Argentina, Bolivia, Czech Republic, Chile, Colombia, Ecuador, the Falkland Islands, French Guiana, Guyana, Paraguay, Peru, South Georgia, the South Sandwich Islands, Suriname, Uruguay, and Venezuela. Western & Central Europe includes  Austria, Belgium, Bulgaria, Croatia, Denmark, Estonia, Finland, France, Hungary, Iceland, Italy, Ireland, Germany, Greece, Latvia, Liechtenstein, Lithuania, Luxembourg, Malta, Monaco, Montenegro, Netherlands, North Macedonia, Norway, Poland, Portugal, Romania, Serbia, Slovakia, Slovenia, Spain, Sweden, Switzerland, Turkey, and the United Kingdom. Other Europe includes Albania, Armenia, Azerbaijan, Belarus, Bosnia and Herzegovina, Georgia,  Kosovo Kazakhstan, Kyrgyzstan, Moldova, Tajikistan, and Ukraine.
